Data Pre-Processing

### 2021-05-18 AST-Framing-Ontario/Data Pre-Processesing.rmd
May 18
- Added Re-trimmed academic papers
- Added excel documenting changes
- Added Original pdf folder

---
title: "Data Pre-Processing"
author: "Jason Lam"
date: "11/03/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
params:
  Academic_Papers: "Texts/Academic Papers NoRef"
  Academic_Papers_DoubCol: "Texts/Academic Papers NoRef DoubleCol"
  Consortia: "Texts/Consortia"
  Municipalities_Regions: "Texts/Municipalities or Regions"
  School Boards: "Texts/School Boards"
  AP_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  AP_DoubCol_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  Con_stopW: c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
  Mun_Reg_stopW: c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
  SB_stopW: c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")

@@

```{r}
pdfLocation <- params$Academic_Papers

@@

pdfLocation <- "Texts/Academic Papers NoRef DoubleCol"

>>>>

---
title: "Data Pre-Processing"
author: "Jason Lam"
date: "11/03/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
params:
  Academic_Papers_SinglCol: "Texts/Academic Papers Trimmed Single Col"
  Academic_Papers_DoubCol: "Texts/Academic Papers Trimmed Double Col"
  Consortia: "Texts/Consortia"
  Municipalities_Regions: "Texts/Municipalities or Regions"
  School Boards: "Texts/School Boards"
  AP_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  AP_DoubCol_stopW: c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")
  Con_stopW: c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")
  Mun_Reg_stopW: c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")
  SB_stopW: c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")

@@

```{r}
pdfLocation <- params$Academic_Papers_SinglCol

@@

pdfLocation <- "Texts/Academic Papers Trimmed Double Col"
